Spatiotemporal Multi-Resolution Approximation of the Amari Type Neural Field Model

### 2012-08-04 Multiresolution_framework/ltx/response_to_reviews.tex

			\item This model cries out for validation in real neuronal systems, but alas, at this point we only see convergence to synthetic data.

			\emph{The authors appreciate that the only way to truly validate the proposed framework is with real data. However, before validating the method on real data we believe that it is essential to first validate the estimation method using accepted models and synthetic data, where the true and estimated parameters can be compared. In an effort to make the method employed in the paper more explicit, we have added ``To illustrate the estimation framework, data is generated using the neural field equations incorporating modeled sensors enabling a comparison between the estimated and true parameters'' to the introduction. We plan to validate the framework on real data in future work. We have added that validating the framework on real data is required in the Conclusion.}

			\item This audience needs to have all symbols, including commonly used ones such as `equality over distribution', double font domains like R and Z, and jargon terms such as `lead field'.

			\emph{\parham{The double font domains are added to Table.1. A brief description of `lead field' is also added below equation (5). *** equality over distribution should be added***}}

@@

			\item Contrasting, for example, this multiresolution method with Freestone's 2011 results would be helpful for continuity.

			\emph{Response here.}

			\item I would also recommend archiving code that, for instance generates figure 11, so that the readership has a chance to replicate these findings, and adapt this method to their own data.

 			\emph{\parham{we have added footnote on page 17 : The Python source code for our numerical simulations is available from the authors on request.}}

### 2012-08-04 Multiresolution_framework/ltx/manuscript.tex
description of lead field
reference for lead field
4.1.6

The observation equation describing the intracranial electrophysiological recordings is given by
\begin{equation}\label{eq:ObservationEquation}
	y_t(\mathbf{r}_{n_y}) = \int_{\Omega} { m\left(\mathbf{r}_{n_y}-\mathbf{r}'\right) v_t\left(\mathbf{r}'\right) \, \mathrm{d}\mathbf{r}'} + \epsilon_t(\mathbf{r}_{n_y}), 
\end{equation}
where $m\left(\mathbf{r}_{n_y}-\mathbf{r}'\right)$ is the observation kernel at location $\mathbf{r}_{n_y}$ and  $\boldsymbol{\epsilon}_{t}\sim \mathcal{N}\left(\mathbf{0},\mathbf{\Sigma}_{\epsilon}\right)$  is an i.i.d. Gaussian white noise process and the covariance matrix $\mathbf{\Sigma}_{\epsilon}=\sigma^2_{\epsilon}\mathbf I_{n_y}$, where $\mathbf I$ denotes the identity matrix. The observation kernel models the pickup range of the electrical fields of the brain. The lead field parameters are not included in the observation equation as the intracranial recordings are considered here. 
\section{MRA of the IDE in State-Space}
The purpose of forming the multi-resolution approximation (MRA) of the integro-difference equation (IDE) is to form a multi-resolution finite-dimensional state-space model that best captures the spatiotemporal characteristics of the neural field. Given such a model, it is then possible to perform state and parameter estimation in an efficient and robust manner, thus allowing for subject-specific models. The goal of this section is to demonstrate how to formulate a state-space model in a canonical form such that standard algorithms may be applied to estimate the multi-resolution connectivity structure.

@@

To demonstrate the performance of the MRAIDE estimation framework, data was generated synthetically  using Eqs.~\eqref{eq:DiscreteTimeModel} and \eqref{eq:ObservationEquation}, allowing a comparison between true and estimated parameters. In doing so, the membrane time constant was set to $\tau = 10$~ms \citep{David2003}, and the sampling time was chosen ten times faster \citep{Stephan2008}, i.e. $T_s = 1$~ms, ensuring the discrepancy between the continuous neural field model and its discrete approximation is small. The connectivity kernel used for data generation composed of two B-spline scaling functions at $j=0$ and $j=1$ forming a compact support Mexican hat shape 

>>>>

The observation equation describing the intracranial electrophysiological recordings is given by
\begin{equation}\label{eq:ObservationEquation}
	y_t(\mathbf{r}_{n_y}) = \int_{\Omega} { m\left(\mathbf{r}_{n_y}-\mathbf{r}'\right) v_t\left(\mathbf{r}'\right) \, \mathrm{d}\mathbf{r}'} + \epsilon_t(\mathbf{r}_{n_y}), 
\end{equation}
where $m\left(\mathbf{r}_{n_y}-\mathbf{r}'\right)$ is the observation kernel at location $\mathbf{r}_{n_y}$ and  $\boldsymbol{\epsilon}_{t}\sim \mathcal{N}\left(\mathbf{0},\mathbf{\Sigma}_{\epsilon}\right)$  is an i.i.d. Gaussian white noise process and the covariance matrix $\mathbf{\Sigma}_{\epsilon}=\sigma^2_{\epsilon}\mathbf I_{n_y}$, where $\mathbf I$ denotes the identity matrix. The observation kernel models the pickup range of the electrical fields of the brain. The lead field parameters are not included in the observation equation as the intracranial recordings are considered here. \parham{The lead field parameters incorporate all the information about the head model, and must be accounted for inverse solutions when scalp electrodes are considered \cite{Jirsa2007}.} 
\section{MRA of the IDE in State-Space}
The purpose of forming the multi-resolution approximation (MRA) of the integro-difference equation (IDE) is to form a multi-resolution finite-dimensional state-space model that best captures the spatiotemporal characteristics of the neural field. Given such a model, it is then possible to perform state and parameter estimation in an efficient and robust manner, thus allowing for subject-specific models. The goal of this section is to demonstrate how to formulate a state-space model in a canonical form such that standard algorithms may be applied to estimate the multi-resolution connectivity structure.

@@

To demonstrate the performance of the MRAIDE estimation framework, data was generated synthetically  using Eqs.~\eqref{eq:DiscreteTimeModel} and \eqref{eq:ObservationEquation}, allowing a comparison between true and estimated parameters \footnote{The Python source code for our numerical simulations is available from the authors on request.}. In doing so, the membrane time constant was set to $\tau = 10$~ms \citep{David2003}, and the sampling time was chosen ten times faster \citep{Stephan2008}, i.e. $T_s = 1$~ms, ensuring the discrepancy between the continuous neural field model and its discrete approximation is small. The connectivity kernel used for data generation composed of two B-spline scaling functions at $j=0$ and $j=1$ forming a compact support Mexican hat shape 
